%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Analytics}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Lead Engineer in Device Analytics} % Job title
    {\href{https://www.micron.com}{Micron Technology}} % Organization
    {Boise, ID} % Location
    {January 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architect Parametric data pipeline including tester output, data transfer/storage, database/API access, report generation, and notification.}
        \item {Reverse-engineer datacenter attacks on Rowhammer vulnerability. Develop mitigation techniques based on novel Markov-Chain model.}
        \item {Overhaul of Python and JMP analysis scripts for reliability and throughput. Resulting report is first-look analysis for all new devices.}
        \item {Evaluate next generation of Parametric Test tools for electrical, parallel test, and software capability.}
        \item {Develop Monte-Carlo simulation model to make automated decisions about wafer health. In process of implementation in Fab environment.}
        \item {Graph-theoretic analysis of failure nodes in novel structure led to simple estimates of failure rate. Analysis completed before production started.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Characterization Engineer} % Job title
    {} % Organization
    {} % Location
    {November 2015 - January 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed a custom worker queue using Flask, Redis, RabbitMQ to provide data/analysis on demand, became the authoritative report for the project.}
        \item {Implement novel measurement techniques to capture high-speed electrical events on experimental devices.}
        \item {Integrate tool operation with Fab Communication system for auotmated operation and increased throughput.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Characterization Intern} % Job title
    {} % Organization
    {} % Location
    {May 2015 - October 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Enable control of new instruments by developing Python drivers to communicate through GPIB interface.}
        \item {Develop desktop application for creating/executing test sequences, now the standard bench characterization platform at Micron.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
