%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Leadership}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Device Analytics Team Lead} % Job title
    {} % Organization
    {} % Location
    {2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Travel to Italy resulted in a new functional team across US, India, Italy dedicated to parametric test data pipeline and analysis.}
        \item {Coordinate high-performing, experienced developers across geographic and language barriers.}
        \item {Pioneer ``dotted-line" reporting within Micron, bringing multiple sites under one functional umbrella. Our success was a factor in Micron's decision to open a new site in Hyderabad.}
        \item {Lead by example when creating documentation, creating one of Micron's most-accessed Confluence pages.}
      \end{cvitems}
    }
  \cventry
    {Micron Software Developers Group - Committee Member} % Job title
    {} % Organization
    {} % Location
    {2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Representative for Inner Source and Forum, championing Open Source practices for Micron internal software.}
        \item {Presentations to Python User Group focusing on code packaging, testing, and deployment.}
        \item {Wrote and taught ``Getting Started with Python" training series, covering basics, data analysis, APIs, multiprocessing, and package creation.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
